Replication of Gantman et al. 2024

### 2024-02-23 manuscript.qmd
rt analysis

>>>>

```{r}
#| label: Compute response time differences for words
#| include: false

subject_level_rt <- behavioral_data_test_set %>%
  filter(correct == TRUE) %>%
  group_by(subject_id, word_category, category, is_word) %>%
  summarize(rt = mean(rt, na.rm = TRUE))
```

```{r}
behavioral_pop_out_data <- subject_level_rt %>%
  filter(is_word == TRUE)

ggplot(behavioral_pop_out_data, aes(x=word_category, y=rt, group=subject_id))+
  geom_point()+
  geom_line()+
  #labs(x="Word Type", y="Accuracy")+
  facet_grid(.~category)+
  theme_bw()
```

```{r}
m <- gee(rt ~ word_category,
    id = subject_id,
    subset = is_word == TRUE & correct == TRUE & category == "moral",
    data = behavioral_data_test_set,
    family = gaussian,
    corstr = "exchangeable")
